\texttt{davos}: a Python package ``smuggler'' for constructing lightweight reproducible notebooks

### 2022-10-19 paper/main.tex
removed hyperlinks from impacts section and unitalicize course name

Since its initial release, \texttt{davos} has found use in a variety
of applications. In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming courses such as
\href{https://github.com/ContextLab/storytelling-with-data}{\textit{Storytelling
    with Data}}~\cite{Mann21b} (an open course on data science,
visualization, and communication) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
{\texttt{abstract2paper}}~\cite{Mann21a} (an example application of
\href{https://github.com/EleutherAI/gpt-neo}{GPT-Neo}) to share
ready-to-run code that installs dependencies automatically.

>>>>

Since its initial release, \texttt{davos} has found use in a variety
of applications. In addition to managing computing environments
for multiple ongoing research studies, \texttt{davos} is being used by
both students and instructors in programming courses such as
Storytelling with Data~\cite{Mann21b} (an open course on data science,
visualization, and communication) to simplify distributing lessons and
submitting assignments, as well as in online demos such as
\texttt{abstract2paper}~\cite{Mann21a} (an example application of GPT-Neo)
to share ready-to-run code that installs dependencies automatically.
